---
title: "Analysis"
format: html
---

[Link to Github](https://github.com/safiaread/homework-1)

https://github.com/safiaread/homework-1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

# Enrollment Data

1. How many observations exist in your current dataset?

```{r, echo=FALSE}
data <- readRDS("/Users/safiaread/Desktop/homework_1/data/output/full_ma_data.rds")
data <- data %>%
subset(year > 2009)
nrow(data)
```

2. 
How many different plan_types exist in the data?
```{r, echo = FALSE}
unique(data$plan_type)
```

3. Provide a table of the count of plans under each plan type in each year. 
Your table should look something like Table 1.

```{r, echo = FALSE}
data %>%
subset(select = c(plan_type, year))%>%
group_by(plan_type, year)%>%
count()%>%
pivot_wider(names_from = year, values_from = n)

#na.rm = T to get rid of NAs
```

4.Remove all special needs plans (SNP), employer group plans (eghp), and all “800-series” plans. 
Provide an updated version of Table 1 after making these exclusions.

```{r, echo = FALSE}
q4 <- data %>%
subset(snp == "No" & eghp == "No", select = c(plan_type, year))%>%
group_by(plan_type, year)%>%
count()%>%
pivot_wider(names_from = year, values_from = n)

q4

#find what 800 series plans are
```

5. Merge the contract service area data to the enrollment data, and restrict the data only to contracts that are approved in their respective counties. 
The R script to create the service area dataset is here: Contract Service Area. 
And you can follow the _BuildFinalData.R script to see where/how I join the datasets. 
Limiting your dataset only to plans with non-missing enrollment data, provide a graph showing the average number of Medicare Advantage enrollees per county from 2010 to 2015. 
Be sure to format your graph in a meaningful way.

```{r, echo = FALSE}
service <- readRDS("/Users/safiaread/Desktop/homework_1/data/output/contract_service_area.rds")
joined <- q4 %>%
  inner_join(service, by=c("plan_type"))
head(joined)
#ggplot()
```

# Premium Data

6.
I am still working on how to merge this data.
```{r}
#
```

7.
I am still working on the graph for this data.
```{r}
#
```

# Summary Questions

8.
I couldn't find what variable stored the information about 800 series data, so I am unsure about why we would ommit them. Perhaps they contained a lot of NAs.

9.
Maybe they charged $0 because they had really high deductibles. They also could have contracts with a small network of providers with high out of pocket costs.

10.
With this data, it was definately an adjustment to manipulate it in VSCode. I have previously used RStudio, and I think you were right that this is a less intuitive interface. I had trouble figuring out how to view the data to get a grasp of how to manipulate it. I also have never worked with a dataset so large before, so it took some time to figure out how to upload it to my computer and organize everything so my computer would run. I'm still having some trouble figuring out the best ways to view the variables and merge them, and the relative paths aren't working for now. 